%
% Copyright © 2014 Peeter Joot.  All Rights Reserved.
% Licenced as described in the file LICENSE under the root directory of this GIT repository.
%
%----------------------------------------------------------------------------------------
%\part{Notes and Problems}
   \mychapter{Nodal analysis.}
   \index{nodal analysis}
      \input{multiphysicsL1.tex}
      \input{multiphysicsL2.tex}
      \input{multiphysicsL3.tex}
   \mychapter{Solving large systems.}
   \index{large systems}
      \input{multiphysicsL4.tex}
      \section{Problems.}
         \input{multiphysicsProblemSet1Problem1.tex}
         \input{multiphysicsProblemSet1Problem2.tex}
         \input{multiphysicsProblemSet1Problem3.tex}
   \mychapter{Numerical errors and conditioning.}
   \index{numerical error}
   \index{conditioning}
      \input{multiphysicsL5.tex}
   \mychapter{Singular value decomposition, and conditioning number.}
   \index{singular value decomposition}
   \index{conditioning number}
      \input{multiphysicsL6.tex}
   \mychapter{Sparse factorization.}
   \index{sparse factorization}
      \input{multiphysicsL7.tex}
   \mychapter{Gradient methods.}
   \index{gradient methods}
      \input{multiphysicsL7B.tex}
      \input{multiphysicsL8.tex}
      \input{multiphysicsL9.tex}
      \section{Problems.}
         \input{multiphysicsProblemSet2aProblem1.tex}
   \mychapter{Solution of nonlinear systems.}
   \index{nonlinear systems}
      \input{multiphysicsL10.tex}
      \input{multiphysicsL11.tex}
      \input{multiphysicsL12DampedNewtons.tex}
      \input{multiphysicsL13SingularJacobian.tex}
      %\mychapter{Struts and Joints, Node branch formulation}
      \section{Struts and Joints, Node branch formulation.}
      \index{strut}
      \index{joint}
      \index{node branch formulation}
      \input{multiphysicsL12.tex}
      \section{Problems.}
         \input{multiphysicsProblemSet2bProblem1.tex}
         \input{multiphysicsProblemSet2bProblem2.tex}
   \mychapter{Time dependent systems.}
   \index{time dependence}
      \input{multiphysicsL13.tex}
      \input{multiphysicsL14.tex}
      \input{multiphysicsL15.tex}
      \input{multiphysicsL16.tex}
      \input{multiphysicsL17.tex}
      \section{Problems.}
         \input{multiphysicsProblemSet3aProblem1.tex}
   \mychapter{Model order reduction.}
   \index{model order reduction}
      \input{multiphysicsL17ModelOrder.tex}
      \input{multiphysicsL18.tex}
      \input{multiphysicsL19.tex}
      \input{multiphysicsL20.tex}
      \section{Problems.}
         \input{multiphysicsProblemSet3bProblem1.tex}
   \mychapter{Harmonic Balance.}
   \index{harmonic balance}
\withproblemsets{
      \section{Final Project.}
         This chapter contains the contents of the project report for the Harmonic Balance topic, describing joint work of
         Michael Royle, an M.A.Sc. Student in the Electromagnetics Group, and myself (Peeter).  An overview of this work
         is also available in presentation format \citep{mikeAndPeeterHBpresentation}.
      \section{Abstract.}
      \input{HarmonicBalanceAbstract.tex}
      \input{HarmonicBalanceText.tex}
}
